%*******************************************************
% Acknowledgements
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{acknowledgments}

\begin{flushright}{\slshape    
    We have seen that computer programming is an art, \\ 
    because it applies accumulated knowledge to the world, \\ 
    because it requires skill and ingenuity, and especially \\
    because it produces objects of beauty.} \\ \medskip
    --- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
\end{flushright}


\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}
First and foremost I offer my sincerest gratitude to my supervisor, Thomas Olof Pederson, who has supported me throughout my thesis with his patience, knowledge, continuous involvement and tireless help, whilst allowing me the room to work in my own way. His useful remarks and engagement through this master thesis helped in shaping the quality of this work. Without him, this thesis would have not been possible.\\

Thanks to Domi\c tian T\u ama\c s-Selicean for the reviews and advices throughout the thesis, but also for the encouragements throughout my studies at the ITU. Thanks to Dan Br\^{a}nda for helping out to get better environment models. Without his help, the 3D models in this thesis would have not been of the same quality. Also, I would like to thank all the participants of the survey, who have willingly shared their precious time during the evaluation process.\\

I would like to thank Jakob Bardram and Mads Frost, which I had the honour to work with, for the opportunity to get hands-on experiences with developing pervasive systems. The work we have done together remains by far one of the most interesting and important projects I have been involved with throughout my career as a software engineer. Furthermore, thanks to the members of the pitLab for their friendship and for the utterly professional environment. These experiences, together with my thesis, made my life as a student at the ITU not only extremely interesting, but also inspiring due to all these exceptional people I have been in touch with.\\

Furthermore, I want to thank my parents for all the support they have provided throughout all of my studies and my life, for their encouragements, appreciation, sacrifices and love. I want to thank my sister, brother, family and friends for always being there for me.\\

Finally, I want to express my deepest love and appreciation to my life partner, C\u at\u alina Borotici, for all the encouragement, support, kindness and unlimited understanding she has offered me throughout my studies. I will be forever grateful for your love.

\bigskip

% \noindent\emph{Regarding \mLyX}: The \mLyX\ port was intially done by 
% \emph{Nicholas Mariette} in March 2009 and continued by 
% \emph{Ivo Pletikosi\'c} in 2011. Thank you very much for your 
% work and the contributions to the original style.


\endgroup



