%************************************************
\section{Scenario 3: Childproof} % (fold)
\label{sec:eval_childproof_scenario}
%************************************************
The hypothetical problem we are facing as part of this task is that families cannot make their homes secure enough for their children. To provide a solution for this problem, there's a need for a system to constantly monitoring the objects a child should keep away from and should not be interacting with. Based on this context information, we can further build various software service to secure the house from the child's actions. One example of such service is the ''Secure Outlets Service'' (SOS). This service has to detect whenever a child is approaching an outlet with a small object, in which case it should shut down the electricity switch for outlets, preventing the child from the possibly of getting electrocuted.\\

For this task, please imagine yourself as being the researcher in charge to develop this system. Once again, you decide to design your system based on the egocentric interaction paradigm, as it can categorizes all the objects of interest around the human agent. In order to validate your design, you decide to simulate the system first.\\

In this exercise, you will be provided with the virtual model of the simulated environment in the Blender\cite{blender:online} format. Blender is a free and open-source software for creating 3D virtual models, animations and more.\\

Using the EgoSim framework, you will augment this model to monitor the objects required by your system. Afterwards, based on the frameworks API, you will write the condition for the SOS to shut the electricity down in the outlets.\\

Next, please follow the steps in the User Guide \ref{ch:user_guide} to set up a new simulation.\\

After you have successfully set up and ran the simulation, as part of the interactions you do with the environment, pick up the Pen from the table and move with it close to one of the outlets, so that the Outlet is in the ActionSpace. When you arrive to this point, you have successfully performed the task.
% section eval_childproof_scenario (end)