%************************************************
\chapter{Evaluation \& Discussion}\label{ch:evaluation}
%************************************************
We have recruited a total of 17 participants, out of which 12 male and 5 female. All of them experienced Software Engineers, one Post-Doctoral Researcher and on Associate Professor. Their average experience in software engineering 6.41 years, with an average of 1.56 year of experience in mobile development. 47.1\% are familiar with concepts context-aware computing, while only 29.4\% have actually worked on context-aware systems. Finally, one participant was familiar with concepts of the egocentric interaction paradigm or the SSM.\\

Our objective with this project was to design and implement an open-source simulation framework that can help developers of mobile context-aware systems to explore design alternatives. The framework was to dynamically classify physical objects, virtual objects and mediators that are close to the human agent according to the situative space model, with the human agent represented as an avatar that can move around and perform basic interaction with objects in the simulated environment.\\

In Section \ref{subsec:user_roles} we have identified three User Roles for the EgoSim framework. To evaluate to what extent we have met the goals defined in Section \ref{sec:goal}, we conducted an evaluation in two parts. First we have evaluated a simulation created with the EgoSim framework from the simulation user's perspective. The users were able to explore a ready made simulation while observing contextual changes in the context client. Second, we have evaluated the EgoSim framework from the system designer's perspective, as the users build a simulation using our framework. Moreover, to determine how our system is different from existing system, we have compared EgoSim to two of the most relevant systems in the related work.\\

\input{Chapters/Chapter05/Participants}
\input{Chapters/Chapter05/Procedure}
\input{Chapters/Chapter05/Discussion}
\input{Chapters/Chapter05/Comparison}
\input{Chapters/Chapter05/Conclusion}