%************************************************
\chapter{Introduction}\label{ch:introduction}
%************************************************

Before the early 1970s, computers were owened by large institutions like corporations, universities or government agencies. These machines, alos know as \emph{Mainframes}, were costly and space consuming, most institutions owning only one piece of such equipment. Lacking any kind of user interface, Mainframes would accept jobs in the form of punched cards, an early input mechanism for data and programs into computers. A group of people in the institutions were instructed how to use the machines (creating punched cards, operating the machines) and they represented the interface between everyday users and the Mainframe. Quite a bottleneck!\\

In 1971 the first commertial microprocessor was released, representing the rise of a new era: the Personal Computer (PC). The PC represented a huge step forward, offering in perspective the possibility for anyone to own a computer and to operate it using novel input/output mechanism: graphical user interface, mouse, keyboard and other peripherals. This is the standard PC setup that we know and, after such o along time, still use. By this I want to point that although we have came a long way, by hardware and software advancements, the human computer interaction (HCI) form that is mostly used to interact with PCs is just as it was envisioned a little more than 40 years ago.\\

The PCs revolution was followed by the idea of portable personal devices like laptops, dynabooks (an educatoinal device simmilar to a nowadays tablet). Although novel at that time, all the fever generated by this revolution was viewed by a group of people at PARC\footnote{Palo Alto Research Center} as being ephemeral: \"[...] My colleagues and I at PARC think that the idea of a \"personal computer\" itself is misplaced, and that the vision of laptop machines, dynabooks and \"knowledge navigators\" is only a transitional step toward achieving the real potential of information technology. Such machines cannot truly make computing an integral, invisible part of the way people live their lives. Therefore we are trying to conceive a new way of thinking about computers in the world, one that takes into account the natural human environment and allows the computers themselves to vanish into the background\". \cite{weiser1991computer}. This futuristic concept envisioned at PARC which further shaped the way we see and use technology and devices is known as \emph{ubicomp}\footnote{Ubiquitous Computing}.\\

\input{Chapters/Chapter01/ProblemStatement}

\input{Chapters/Chapter01/Goal}

\input{Chapters/Chapter01/Method}

\input{Chapters/Chapter01/ThesisOverview}

